%%%%%%%%%%%%
%
% $Autor: Wings $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: FirstStep.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{First Step}

\section{Accessing the Application}
The Stock Predictor application is deployed on a secure cloud platform and does not require installation on the user's local machine. It can be accessed directly through any supported web browser.

\subsection{Opening the Platform}
Users can begin by navigating to the application link provided by the project administrator or hosting environment. This link opens a responsive web-based dashboard that serves as the main interface for interaction.

\subsection{User Interface Initialization}
Upon loading, the browser automatically initializes the platform's components. This includes model loading, data connection setup, and preparation of interactive widgets. Depending on internet speed and system responsiveness, this initialization may take a few seconds during the first use.


\section{No Setup or Installation Required}
The entire application is managed in the cloud. Users do not need to download, configure, or install any software packages. All computations—including data preprocessing, model execution, evaluation, and plotting—are performed on the backend servers.

As a result, the user experience is consistent across devices and operating systems. The system is ready to use immediately after the web page is opened, allowing users to focus on forecasting tasks without any technical setup or overhead.

