%%%%%%%%%%%%
%
% $Autor: Wings $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: Maintenance.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Maintenance}

\section{System Monitoring and Logging}
The cloud-hosted Stock Predictor application includes an integrated monitoring system to ensure stability, detect anomalies, and support issue resolution.

\subsection{Purpose}
The internal monitoring infrastructure records key application events such as model executions, forecasting outcomes, and system-level errors. This functionality is critical for identifying issues related to data access, prediction anomalies, or service disruptions. It also supports diagnostic reviews by the development team to improve future performance and robustness.

\subsection{User Visibility}
Users receive immediate feedback through on-screen alerts or informational messages within the Graphical User Interface (GUI). These notifications cover scenarios such as invalid date selections, unavailable data, or missing model selections. In case of a critical failure, a descriptive error message is displayed to guide the user without exposing technical details.

\section{Application Updates}
The application is maintained through a centralized deployment system that ensures all users operate on the most recent and stable version. Since the application is web-based, updates are handled automatically on the server side.

\subsection{Update Lifecycle}
Improvements to model accuracy, performance enhancements, interface changes, and bug fixes are deployed periodically. Updates do not require any action from the user. Once changes are published to the cloud environment, all users accessing the platform benefit from the enhancements in real time.

\subsection{No Manual Installation Required}
Because the application is hosted online, users do not need to download or install any files. This removes the burden of managing software versions or manually replacing outdated builds. The web-based architecture ensures seamless upgrades and uniform user experience across different sessions and devices.




