%%%%%%%%%%%%
%
% $Autor: Wings $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: Troubleshooting.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Troubleshooting}

\section{Application Fails to Load in Browser}
If the application does not load properly or remains stuck on the initial screen:

\subsection{Possible Causes}
\begin{itemize}
	\item A slow or unstable internet connection may prevent the application from retrieving data.
	\item The browser may be using an unsupported version or have JavaScript disabled.
	\item Temporary server issues may affect availability.
\end{itemize}

\subsection{Recommended Actions}
\begin{itemize}
	\item Ensure you are connected to a reliable internet network.
	\item Use a supported and updated web browser such as Google Chrome, Mozilla Firefox, or Microsoft Edge.
	\item Refresh the browser page or clear the cache and try again after a few minutes.
	\item If the issue persists, check for platform-specific service announcements.
\end{itemize}

\section{Prediction Does Not Trigger}
If clicking the ``Predict'' button does not produce any output:

\subsection{Likely Causes}
\begin{itemize}
	\item No forecasting model has been selected.
	\item An invalid date was chosen (e.g., a weekend or a public holiday).
\end{itemize}

\subsection{Suggested Fixes}
\begin{itemize}
	\item Select a valid model from the dropdown list, either Long Short-Term Memory (LSTM) or AutoRegressive Integrated Moving Average (ARIMA).
	\item Make sure the selected date corresponds to a valid trading day.
\end{itemize}

\section{Unexpected or Missing Results}
If the predicted values appear to be incorrect or are not displayed at all:

\subsection{Potential Reasons}
\begin{itemize}
	\item The selected date may be too close to the current day, leading to insufficient prior data.
	\item For LSTM forecasts, the required input sequence of 60 prior trading days may not be available due to data gaps.
	\item The financial data provider may not have released data for the selected day yet.
\end{itemize}

\subsection{Resolution Steps}
\begin{itemize}
	\item Choose a date that is at least one trading day ahead and well-supported by historical data.
	\item Prefer dates for which financial markets have already closed and official data is likely available.
	\item For Long Short-Term Memory (LSTM) forecasts, ensure at least 60 valid consecutive trading days precede the selected date.
\end{itemize}

\section{Performance and Compatibility Issues}
If the interface becomes slow, unresponsive, or visually distorted:

\subsection{Possible Causes}
\begin{itemize}
	\item The browser session may be overloaded with cached data or extensions.
	
\end{itemize}

\subsection{Solutions}
\begin{itemize}
	\item Try restarting your browser or switching to a different supported browser.
	\item Close other tabs or applications running in the background to free up memory.
\end{itemize}






